RTaxonWorks
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/RTaxonWorks)](https://cranchecks.info/pkgs/RTaxonWorks)
[![R-CMD-check](https://github.com/SpeciesFileGroup/RTaxonWorks/workflows/R-CMD-check/badge.svg)](https://github.com/SpeciesFileGroup/RTaxonWorks/actions)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/RTaxonWorks)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/RTaxonWorks)](https://cran.r-project.org/package=RTaxonWorks)

`RTaxonWorks` is a R client for the TaxonWorks API

Package documentation: https://docs.taxonworks.org/r

* TaxonWorks: https://taxonworks.org
* TaxonWorks GitHub repository: https://github.com/SpeciesFileGroup/taxonworks
* TaxonWorks API docs: https://api.taxonworks.org
* TaxonWorks documentation: https://docs.taxonworks.org
## Installation

```{r eval=FALSE}
install.packages("RTaxonWorks")
```

Load the package
```{r}
library("RTaxonWorks")
```

Dev version

Read the [CONTRIBUTING guide](CONTRIBUTING.md) to install the development version.



## Meta

* Please [report any issues or bugs](https://github.com/SpeciesFileGroup/RTaxonWorks/issues).
* License: NCSA
* Get citation information for `RTaxonWorks` in R doing `citation(package = 'RTaxonWorks')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
