RTaxonWorks
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/RTaxonWorks)](https://cranchecks.info/pkgs/RTaxonWorks)
[![R-CMD-check](https://github.com/SpeciesFileGroup/RTaxonWorks/workflows/R-CMD-check/badge.svg)](https://github.com/SpeciesFileGroup/RTaxonWorks/actions)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/RTaxonWorks)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/RTaxonWorks)](https://cran.r-project.org/package=RTaxonWorks)

`RTaxonWorks` is an R client for the [TaxonWorks](https://taxonworks.org) API. Code follow the spirit/approach of the Gem [rcol](https://github.com/sckott/rcol), and indeed much of the wrapping utility is copied 1:1 from that repo, thanks [@sckott](https://github.com/sckott).


Package documentation: https://docs.taxonworks.org/r

* TaxonWorks: https://taxonworks.org
* TaxonWorks GitHub repository: https://github.com/SpeciesFileGroup/taxonworks
* TaxonWorks API docs: https://api.taxonworks.org
* TaxonWorks documentation: https://docs.taxonworks.org

## Installation

```{r eval=FALSE}
install.packages("RTaxonWorks")
```

Load the package
```{r}
library("RTaxonWorks")
```

Dev version

## Contributing

Bug reports and pull requests are welcome on GitHub at https://github.com/SpeciesFileGroup/RTaxonWorks. This project is intended to be a safe, welcoming space for collaboration, and contributors are expected to adhere to the [code of conduct](https://github.com/SpeciesFileGroup/RTaxonWorks/blob/main/CODE_OF_CONDUCT.md).

## Development

Please read the [CONTRIBUTING guide](CONTRIBUTING.md) for instructions on how to install the development version.

## License

The gem is available as open source under the terms of the [NCSA/Illinois](https://github.com/SpeciesFileGroup/RTaxonWorks/blob/main/LICENSE.txt) license. You can learn more about the NCSA license on [Wikipedia](https://en.wikipedia.org/wiki/University_of_Illinois/NCSA_Open_Source_License) and compare it with other open source licenses at the [Open Source Initiative](https://opensource.org/license/uoi-ncsa-php/).

## Code of Conduct

Everyone interacting in the RTaxonWorks project's codebases, issue trackers, chat rooms and mailing lists is expected to follow the [code of conduct](https://github.com/SpeciesFileGroup/RTaxonWorks/blob/main/CODE_OF_CONDUCT.md).
